\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-03-03 fluB.tex
Add a blurb under dTMRCA figure supplements.

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_trees.png}
\caption{\textbf{Mean $\dtmrca$ between all pairs of trees of segments.}}
\label{deltaTMRCAtrees}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_replicates.png}
\caption{\textbf{Mean $\dtmrca$ between replicate trees of each segment.}}
\label{deltaTMRCAreplicates}
\end{figure}

>>>>

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_trees.png}
\caption{\textbf{Mean $\dtmrca$ between all pairs of trees of segments.}
Mean $\dtmrca$ between trees of segments reveal that tip pairs in PB1, PB2 and HA trees have very similar TMRCAs.
The upper tail of the 95\% HPD (HPDs are represented as vertical lines) interval of mean $\dtmrca$ values for PB1-PB2-HA and MP-NA trees do not exceed 3 years.}
\label{deltaTMRCAtrees}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_replicates.png}
\caption{\textbf{Mean $\dtmrca$ between replicate trees of each segment.}
Mean $\dtmrca$ values between independent analyses of each segment show that mean $\dtmrca$ values rarely exceed 1 year.}
\label{deltaTMRCAreplicates}
\end{figure}
